Tropical Andes plant trait data BIEN

### 2023-07-18 code/L0/L0_TropicalAndes_plants_BIEN_traits.Rmd
add summary, fill in overview, add title, save output to csv

---
title: ""
author: "Hazel J. Anderson"
project: "Plant-Frugivore Diversity"
collaborators: "Beth E. Gerstner, Phoebe L. Zarnetske"
overview: ""
data input: ""
data output: ""
date: "2023-07-18"
output: html_document
---

@@

```{r}

```

# Write data to csv
```{r}
TropicalAndes_BIEN_traits_path <- file.path(output_path,"TropicalAndes_BIEN_traits.csv") 
write.csv(TropicalAndes_BIEN_traits, file = TropicalAndes_BIEN_traits_path)
```

>>>>

---
title: "Tropical Andes plant trait data BIEN"
author: "Hazel J. Anderson"
project: "Plant-Frugivore Diversity"
collaborators: "Beth E. Gerstner, Phoebe L. Zarnetske"
overview: "This script retrieves plant trait data from the BIEN database for plant species in the countries that make up the Tropical Andes."
data input: "none"
data output: "TropicalAndes_BIEN_traits.csv"
date: "2023-07-18"
output: html_document
---

@@

```{r}
print("The number of records is")
nrow(TropicalAndes_BIEN_traits)
print("The number of species is")
length(unique(TropicalAndes_BIEN_traits$scrubbed_species_binomial))
print("The number of families is")
length(unique(TropicalAndes_BIEN_traits$family_matched))
```

# Write data to csv
```{r}
TropicalAndes_BIEN_traits_path <- file.path(output_path,"TropicalAndes_BIEN_plant_traits.csv") 
write.csv(TropicalAndes_BIEN_traits, file = TropicalAndes_BIEN_traits_path)
```
